---
title: "Final Exam"
author: "Reginald Mordi"
date: "December 1"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

***
### we depend on 3 variables GPA, Work Experience, and GRE Score
### There is a score for each student 
### Scare can be calculated by multiplying the 3 values of variables 
### then we form the lp file with those scorers

The objective function is to maximize the scores of the students
,while each student can be chosen only once.


The mathematical model

min X X c y þ X wP.zU — zLΣ þ wNðvU — vLÞ

s:t: X xij ¼ 1	8j

yjk—xij—xik	≤	—1	8j; k; i	(2)

vi—	xij	¼	0  8i	(3)

zli— X aljxij	¼	0 8i; l	(4)

vL ≤ vi ≤ vU	8i	(5)

zL ≤ zli ≤ zU	8i; l	(6)

xij 2 f0; 1g	8i; j	(7)

yjk 2 f0; 1g	8j; k	(8)

zli ≤ 0	8i; l	(9)

vi ≤ 0	8i	(10)

zL; zU ≤ 0	8l	(11)

vL; vU ≤ 0	(12)


## Read the lp file>>>
```{r}
library(lpSolveAPI)
x <- read.lp("Final.lp")
x
```


```{r}
solve(x)
get.objective(x)
get.variables(x)
get.constraints(x)
get.sensitivity.objex(x)
```

*** 
The groups are:

Group 1.	X11, x61, x91       Students number(1,6,9)

Group 2.	X72, x112, x122     Students number(7,11,12)

Group 3.	X33, x43, x103      Students number(3,4,10)

Group 4.	X24, x54, x84       Students number(2,5,8)

***