---
title: "Assignment Module 4"
author: "Reginald Mordi"
date: "10/2/2020"
output: html_document

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

#This notebook contains the code for question number 3 in the assignment 2. Specifically, the formulation for the Weigelt Corporation example

* Note that lines that start with # are comments. 

```{r,eval=FALSE}
#install.packages("lpSolveAPI")
library(lpSolveAPI)
```
***
Let us set up the Weigelt Corporation problem. Note that we had nine decision variables, and nine constraints.
In the first formulation, we will directly create the objective function and constraints
```{r}
# make an lp object with 0 constraints and 9 decision variables
lp <- make.lp(0, 9)

# Now create the objective function. 
set.objfn(lp, c(420, 360, 300, 420, 360, 300, 420, 360, 300))

# It is a maximization problem
lp.control(lp,sense='max')

# Add the nine  constraints
# 3 constrains for Production Capacity of the three plants
add.constraint(lp, c(1, 1, 1, 0, 0, 0, 0, 0, 0), "<=", 750)
add.constraint(lp, c(0, 0, 0, 1, 1, 1, 0, 0, 0), "<=", 900)
add.constraint(lp, c(0, 0, 0, 0, 0, 0, 1, 1, 1), "<=", 450)

# 3 constrains for the in-process storage space available for a day's production of the three plants
add.constraint(lp, c(20, 15, 12, 0, 0, 0, 0, 0, 0), "<=", 13000)
add.constraint(lp, c(0, 0, 0, 20, 15, 12, 0, 0, 0), "<=", 12000)
add.constraint(lp, c(0, 0, 0, 0, 0, 0, 20, 15, 12), "<=", 5000)

# 3 constrains for the Sales Forecasting 
add.constraint(lp, c(0, 0, 1, 0, 0, 1, 0, 0, 1), "<=", 900)
add.constraint(lp, c(0, 1, 0, 0, 1, 0, 0, 1, 0), "<=", 1200)
add.constraint(lp, c(1, 0, 0, 1, 0, 0, 1, 0, 0), "<=", 750)

add.constraint(lp, c(900, 900, 900, -750, -750, -750, 0, 0, 0), "=", 0)
add.constraint(lp, c(450, 450, 450, 0, 0, 0, -750, -750, -750), "=", 0)

# To identify the variables and constraints, we can
# set variable names and names of the constraints

ColNames <- c("P11", "P12", "P13", "P21", "P22", "P23", "P31", "P32", "P33")
RowNames <- c("Capacity-P1", "Capacity-P2", "Capacity-P3", "Storage-P1", "Storage-P2", "Storage-P3", "Sales-P1", "Sales-P2", "Sales-P3","c1","c2")
dimnames(lp) <- list(RowNames, ColNames)

# Now, print out the model
lp

# The model can also be saved to a file
write.lp(lp, filename = "rmordi_4.lp", type = "lp")
```
We now solve the above LP problem

```{r}
solve(lp)
get.objective(lp)
get.variables(lp)
get.constraints(lp)
```
***
# We can see from the above analysis that the maximum Profit that Weigelt Company can achieve according to our constraints is $ 696000.

# It seems that to maximize the profit we do not need large products from plant 1, and no small products form plnat # 2, and no small and medium produts from plant3.

