---
Name: Regie Mordi
Course: QMM Fall 2020
Date: 10/10/2020
title: "Heart Solution"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

***
Heart produces (AEDs) in two different plants (A and B)

Module formulation for the productin and shipping data of Heart Co. is given below, and read through the LP file.

A transportation problem will have feasible solutions if and only if total supply = total demand
In this problem the monthly supply is 220, while the monthly demand is 210, 
So, we will create a dummy destination (dummy warehouse 4) equal to 10 
The Total cost for each unit is (production cost + shipping cost), In addition, we require that the values of the variables be binary 0 (not assigned) of 1 (assigned). Note the use of the big "M" method for costs. The complete formulation is below
```
/* Objective function */
min: 622 A1 + 614 A2 + 630 A3 + 641 B1 + 645 B2 + 649 B3;

/* Constraints */
A1 + A2 + A3 + A4 = 100;
B1 + B2 + B3 + B4 = 120;
A1 + B1 = 80;
A2 + B2 = 60;
A3 + B3 = 70;
A4 + B4 = 10;
```
```{r}
library(lpSolveAPI)
x <- read.lp("Heart.lp")
x
```

```{r}
solve(x)
get.objective(x)
get.variables(x)
```
***
*** From the above solution we can notice that the solve is 0, which means that there is no errors with problem formulation***
*** The minimum Total cost for producing and shipping the units from Plants to Warehouses is $132790.***
*** To achieve the minimum cost the plant A should not produce and ship any unit to warehouse 1 also plant 2 should not produce and ship any unit to plant 2, while we still have dummy units produced from plant 2 to warehouse 4.***