---
title: "Assignment Goal Programming"
author: "Reginald Mordi"
date: "11/4/2020"
Problem: Emax Corporation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

***
# Emax Corporation 

```{r}
library(lpSolveAPI)
Emax <- read.lp("Emax.lp")
Emax
``` 
## Solve
```{r}
solve(Emax)
get.objective(Emax)
get.variables(Emax)
```

### Remarks

Applying the simplex method we can imply that
producing 15 units of production 3 yields the optimal solution of $225 million in profit, but this cased an increase in the levels of employment by 2500 from the current year 5000.

the company is concerned also about the goal of emplyment levels

so we try to achieve this goal also

#Emax co. - Streamlined Approach
***
```{r}
library(lpSolveAPI)
Stream_Emax <- read.lp("Goal_Emax_streamline.lp")
Stream_Emax
``` 

## Solve
```{r}
solve(Stream_Emax)
get.objective(Stream_Emax)
get.variables(Stream_Emax)
```
Here we can notice that the optimal solution is $208.333 million
This solution asure that all goals are met, and the optimal solution falls short of the first-priority goals with respect to long-run profit.

# so the management of the Emax will suggest to produce a mix of the second production by approximatly 8 units and 3 units of the third one
