---
title: "Assignment Module 8_DEA "
author: "Reginald Mordi"
date: "10/28/2020"

---
# Health Company.

```{r}
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,0.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y) <- c("3rd_Party_Reimbursed","Privately_Paid")
colnames(x) <- c("Staff","Supplies")
x
y

```

*** We now run the DEA analysis. ***
```{r}
library(Benchmarking)
FDH <- dea(x,y,RTS = "fdh")            # provide the input and output FDH
FDH

peers(FDH)                             # identify the peers
lambda(FDH)


CRS <- dea(x,y,RTS = "crs")            # provide the input and output 
CRS

peers(CRS)                             # identify the peers
lambda(CRS)


VRS <- dea(x,y,RTS = "vrs")            # provide the input and output 
VRS

peers(VRS)                             # identify the peers
lambda(VRS)



IRS <- dea(x,y,RTS = "irs")            # provide the input and output 
IRS
peers(IRS)                             # identify the peers
lambda(IRS)



DRS <- dea(x,y,RTS = "drs")            # provide the input and output 
DRS

peers(DRS)                             # identify the peers
lambda(DRS)


FRH <- dea(x,y,RTS = "add")            # provide the input and output 
FRH

peers(FRH)                             # identify the peers
lambda(FRH)

```

```{r}
#Creating the data frame
model <- data.frame(FDH=c(1, 1, 1, 1, 1, 1), CRS=c(1, 1, 1, 1, 0.9775, 0.8675), VRS=c(1, 1, 1, 1, 1, 0.8963), IRS=c(1, 1, 1, 1, 1, 0.8963), DRS=c(1, 1, 1, 1, 0.9775, 0.8675), FRH=c(1, 1, 1, 1, 1, 1))

model
All <- cbind(x,y, model)
All

## Compare the results: For FDH every variable was efficient. For CRS, every variable except 5 or 6 was efficient and the benchmarking for both was to 1,2, and 4. For VRS and IRS every variable except 6 was efficient and the benchmarking was to 1, 2, and 5. For DRS the only variables that were not efficient were 5 anf 6. The benchmarking was to 1, 2, and 4. For FRH, every variable was efficient.
```

**Comment**: The results indicate that DMUs (1:6) under the asssumption FDH and FRH are efficient. , CRS, VRS, IRS, DRS, and FRH (1:4) are efficient., and DMU(5) and (6) for CRS and DRS are not while 5 is efficient. for VRS and IRS but 6 is not efficient. for VRS and IRS.

**Comment**: The peer units for the suffient DMU are themselves but for the unsuffient like DMU(6) has peers 1,2,4 for CRS and DRS and 1,2,5 for VRS, IRS

```{r}
library(lpSolveAPI)
Z <- read.lp("Health.lp")
Z
solve(Z)
get.objective(Z)
get.variables(Z)
```

